Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-03-31 README.Rmd
update readme with arxiv citation

>>>>

If you use these scripts, cite this paper:

Nay, John J., Van der Linden, Martin, Gilligan, Jonathan. (2016) "Betting and Belief: Prediction Markets and Attribution of Climate Change." eprint arXiv:1603.08961

The paper can be downloaded here: [http://arxiv.org/abs/1603.08961](http://arxiv.org/abs/1603.08961)
